Kindly Bent to Free Us

### 2019-07-01 kindly/lang.tex
Add syntactic rules for automatic region annotation.
Attempt at typesetting code-as-semrules.
checkpoint
Start writing the text.

\subsection{Syntax}

@@

\clearpage
\subsection{Semantics}
\input{fig-reduction}

\clearpage
\subsection{Typing}

@@

\begin{figure*}[htp]
  \input{infer/sd-typing}
  \caption{Syntax-directed typing rules}
  \label{fig:syntax-directed-typing}
\end{figure*}

\clearpage
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

We now present a formalization of the \lang language featuring
a minimal ML language with let-polymorphism, abstract types, pairs, and our novel
linear type system with borrows which uses kinds and qualified types.
For ease of presentation,
our formalization makes the following simplifications.
First, we only consider matching on pairs, instead of arbitrary algebraic
datatypes. We consider separate operators for borrowing and reborrowing (taking
the borrow of a borrow). We consider regions to be fully annotated
and present a set of rules to infer their placement.
Finally we emulates region variables
as a series of nesting indices.

In the rest of this section, we present the syntax (\cref{syntax}),
a linearity-aware semantics (\cref{sem}), syntax directed typing rules
(\cref{sdtyping}) and automatic rules for region annotations (\cref{regionannot}).

\subsection{Syntax}
\label{syntax}

@@

\clearpage
\subsection{Semantics}
\label{sem}

\input{fig-reduction}
\input{fig-code}

\clearpage
\subsection{Typing}
\label{sdtyping}

@@

\begin{figure*}[tp]
  \input{infer/sd-environments}
  \caption{Rewriting constraints on environments and types}
  \label{fig:contraints-environments-types}
\end{figure*}
\begin{figure*}[tp]
  \input{infer/sd-typing}
  \caption{Syntax-directed typing rules}
  \label{fig:syntax-directed-typing}
\end{figure*}

\clearpage

\subsection{Annotating regions}
\label{regionannot}

\begin{figure*}[htp]
  \centering
  \input{region-annot}
  \caption{Automatic region annotation --- $\Rannot{e}{e'}{B}$}
  \label{fig:region-annotation}
\end{figure*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
